PANCHANGE_data_preprocessing

### 2020-09-15 PANCHANGE_data_preprocessing2020-07-15.Rmd
added difference between start of pandemic and prepandemic sign up questionnaire

Calculate the time difference between starting the COPING questionnaire and the beginning of the pandemic
```{r time difference between starting the COP|NG questionnaire and the beginning of the pandemic}
if(GLAD == TRUE | EDGI == TRUE | RAMP == TRUE | NBR == TRUE){
# using date of pandemic as 23rd of March
dat <- dat %>%
  mutate(
    time_diff_coping_lockdown_march_23 =
        as.numeric(
        difftime(           #this function does time1 - time2 as difftime(time1, time2...)
          startDate.coping,    #should be start date for COPING (time1)
          date_uk_lockdown_march_23),    #should be start date for GLAD (time2)
          units = c("weeks")  #can also be "secs", "mins", "hours", "weeks"
          )
        )

@@

>>>>

Calculate the time difference between starting the COPING questionnaire and the beginning of the pandemic
```{r time difference between starting the COPING questionnaire and the beginning of the pandemic}
if(GLAD == TRUE | EDGI == TRUE | RAMP == TRUE | NBR == TRUE){
# using date of pandemic as 23rd of March
dat <- dat %>%
  mutate(
    time_diff_coping_lockdown_march_23 =
        as.numeric(
        difftime(           #this function does time1 - time2 as difftime(time1, time2...)
          startDate.coping,    #should be start date for COPING (time1)
          date_uk_lockdown_march_23),    #should be start date for GLAD (time2)
          units = c("weeks")  #can also be "secs", "mins", "hours", "weeks"
          )
        )

@@

Calculate the time difference between sign up questionnaire and the beginning of the pandemic
```{r time difference between sign up and the beginning of the pandemic}
if(GLAD == TRUE | EDGI == TRUE){
# using date of pandemic as 23rd of March
dat <- dat %>%
  mutate(
    time_diff_signup_lockdown_march_23 =
        as.numeric(
        difftime(           #this function does time1 - time2 as difftime(time1, time2...)
          date_uk_lockdown_march_23,    # should be start date of the pandemic (time1)
          startDate.prepandemic),    # should be start date for sign up questionnaire EDGI or GLAD (time2)
          units = c("weeks")  #can also be "secs", "mins", "hours", "weeks"
          )
        )

dat %>%
  descr(
    var = time_diff_signup_lockdown_march_23,
    stats = "common"
    )

# using date as 1st of March  
dat <- dat %>%
  mutate(
    time_diff_signup_awareness_march_1 =
        as.numeric(
        difftime(           #this function does time1 - time2 as difftime(time1, time2...)
          date_higher_awareness_march_1,    # should be start date of the pandemic (time1)
          startDate.prepandemic),    # should be start date for sign up questionnaire EDGI or GLAD (time2)
          units = c("weeks")  #can also be "secs", "mins", "hours", "weeks"
          )
        )

dat %>%
  descr(
    var = time_diff_signup_awareness_march_1,
    stats = "common"
    )

dat <- dat %>%
  mutate(
    time_diff_signup_first_case_uk_jan_31 =
        as.numeric(
        difftime(           #this function does time1 - time2 as difftime(time1, time2...)
          date_first_case_uk_january_31,    # should be start date of the pandemic (time1)
          startDate.prepandemic),    # should be start date for sign up questionnaire EDGI or GLAD (time2)
          units = c("weeks")  #can also be "secs", "mins", "hours", "weeks"
          )
        )

dat %>%
  descr(
    var = time_diff_signup_first_case_uk_jan_31,
    stats = "common"
    )
}
```

Testing 3, 6, and 9 months before pandemic
```{r Testing 3, 6, and 6 months before pandemic}
if(GLAD == TRUE | EDGI == TRUE){
dat %>%
  filter(time_diff_signup_lockdown_march_23 < 12) %>%
  nrow()

dat %>%
  filter(time_diff_signup_lockdown_march_23 < 24) %>%
  nrow()

dat %>%
  filter(time_diff_signup_lockdown_march_23 < 36) %>%
  nrow()

dat %>%
  filter(time_diff_signup_awareness_march_1 < 12) %>%
  nrow()

dat %>%
  filter(time_diff_signup_awareness_march_1 < 24) %>%
  nrow()

dat %>%
  filter(time_diff_signup_awareness_march_1 < 36) %>%
  nrow()

dat %>%
  filter(time_diff_signup_first_case_uk_jan_31 < 12) %>%
  nrow()

dat %>%
  filter(time_diff_signup_first_case_uk_jan_31 < 24) %>%
  nrow()

dat %>%
  filter(time_diff_signup_first_case_uk_jan_31 < 36) %>%
  nrow()
}
```
